Something about Performance, 2D Component of NEMO. (TBC)

### 2015-03-10 nemolite2d_perf.tex
Update OMP scaling plots to include parallel efficiency. Add grace files to svn.

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_256_gnu}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Gnu compiler on a single Intel Ivy Bridge
  socket. The 24-thread runs employed hyperthreading and the optimal
  OpenMP schedule is given in parentheses.}
\label{FIG_gnu_omp_256}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_256_intel}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Intel compiler on a single Intel Ivy Bridge
  socket. The 24-thread runs employed hyperthreading and the optimal
  OpenMP schedule is given in parentheses.}
\label{FIG_intel_omp_256}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_256_cray}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Cray compiler on a single Intel Ivy Bridge
  socket. The 24-thread runs employed hyperthreading and the optimal
  OpenMP schedule is given in parentheses.}
\label{FIG_cray_omp_256}
\end{figure}

The final optimisation step found to have any significant effect is to
minimise the amount of thread synchronisation by introducing the
NOWAIT qualifier wherever possible (blue lines). For the Gnu compiler,
this improves the performance of the executable on eight or more
threads while, for the Intel compiler, it only gives an improvement
for the 24-thread case. Moving the SINGLE region before a parallel
loop is marginally beneficial for the Gnu- and Cray-compiled binaries
and yet reduces the performance of the Intel binary (purple lines).

>>>>

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_256_gnu}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Gnu compiler on a single Intel Ivy Bridge
  socket. The corresponding parallel efficiencies are shown using open
  symbols and dashed lines. The 24-thread runs employed hyperthreading
  and the optimal OpenMP schedule is given in parentheses.}
\label{FIG_gnu_omp_256}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_256_intel}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Intel compiler on a single Intel Ivy Bridge
  socket.  The corresponding parallel efficiencies are shown using
  open symbols and dashed lines. The 24-thread runs employed
  hyperthreading and the optimal OpenMP schedule is given in
  parentheses.}
\label{FIG_intel_omp_256}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_256_cray}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Cray compiler on a single Intel Ivy Bridge
  socket.  The corresponding parallel efficiencies are shown using
  open symbols and dashed lines. The 24-thread runs employed
  hyperthreading and the optimal OpenMP schedule is given in
  parentheses.}
\label{FIG_cray_omp_256}
\end{figure}

The final optimisation step that we found to have any significant
effect is to minimise the amount of thread synchronisation by
introducing the NOWAIT qualifier wherever possible (blue lines). For
the Gnu compiler, this improves the performance of the executable on
eight or more threads while, for the Intel compiler, it only gives an
improvement for the 24-thread case. Moving the SINGLE region before a
parallel loop is marginally beneficial for the Gnu- and Cray-compiled
binaries and yet reduces the performance of the Intel binary (purple
lines).
